Awareness and Russellian Epistemology

### 2011-01-30 paper.tex
Changed title

\newcommand{\PP}{\circlearrowleft}
\newcommand{\nmodels}{\nvDash}
\begin{document}

\title{Awareness and Russell's Epistemology}\author{Matthew P.
Wampler-Doty}\date{}\maketitle

\begin{abstract}
This paper presents a novel approach to formulating epistemic directly
in terms of logical inference.  Using awareness logic, $\Box_X \phi$ is
taken to literally mean ``it follows from formulae $X$ is explicitly aware of
that $\phi$''.  This is done by incorporating logic into the semantics
of awareness logic.  Our approach corresponds closely to the framework
for epistemology proposed by Bertrand
Russell\cite{russell_problems_1936}, and illustrates that
objections provided by Jaako Hintikka\cite{hintikka_knowledge_1969} to
the proposed interpretation of epistemic logic should be considered invalid.
\end{abstract}

@@

\subsection{Neighborhood Semantics}
\label{neighborhood_semantics}
\input{neighborhood_semantics.tex}

\subsection{\label{quantifying}Multi-Modal Logic}
\label{modal-modal}
\input{modal-modal.tex}

\section{Conclusions \& Further Research}
\label{conclusions}
\input{conclusions.tex}

>>>>

\newcommand{\PP}{\circlearrowleft}
\newcommand{\nmodels}{\nvDash}
\renewcommand{\models}{\vDash}
\begin{document}

\title{Awareness and Russellian Epistemology}\author{Matthew P.
Wampler-Doty}\date{}\maketitle

\begin{abstract}
This paper presents a novel approach to formulating epistemic directly
in terms of logical inference.  Using variations on awareness logic,
we develop systems where $\Box \phi$ is
literally taken to mean ``it follows from formulae the agent is explicitly aware of
that $\phi$''.  We accomplish this by incorporating logical inference into the semantics
of awareness logic.  Our reading of awareness logic corresponds
closely to a form of \emph{strong foundationalism} proposed by Bertrand
Russell\cite{russell_problems_1936}.  Our findings illustrate that an
objection provided by Jaako Hintikka\cite{hintikka_knowledge_1969} to
the proposed interpretation of epistemic modality is invalid.
\end{abstract}

@@

\subsection{Neighborhood Semantics (Doxastic Logic)}
\label{neighborhood_semantics}
\input{neighborhood_semantics.tex}

% \subsection{\label{quantifying}Multi-Modal Logic}
% \label{modal-modal}
% \input{modal-modal.tex}

\section{Closing Remarks \& Conclusions}
\label{conclusions}
\input{conclusions.tex}
